General constraints on magic distillation protocols from statistical mechanics

### 2021-05-14 magic_paper.tex
some changes
wrap up of findings on phi, F. phi doesnt really tend to infinity

\begin{figure}[t!]
    \centering
    \subfigure[][]{%
    \label{fig:phip}%
    \includegraphics[scale=0.4]{figs/test/phi_p.pdf}}\\
    \subfigure[][]{%
    \label{fig:Rp}%
    \includegraphics[scale=0.4]{figs/test/rate_p.pdf}}
    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = p\ {\rm{diag}}(0,1,2) + (1-p)\ {\rm{Hadamard}}$.
\subref{fig:noCliff} Plot of $\phi$ vs $p$
 \subref{fig:Cliff} Plot of $R$ vs $p$}
    \label{fig:vsp}
\end{figure}

Performing the standard 3D-rotation matrix 
\begin{equation}
\begin{pmatrix}
\sin{\theta}\cos{\varphi} & \sin{\theta}\sin{\varphi} & \cos{\theta}\\
\cos{\theta}\cos{\varphi} & \cos{\theta}\sin{\varphi} & -\sin{\theta}\\
-\sin{\varphi} & \cos{\varphi} & 0
\end{pmatrix}
\end{equation}
on $H$ to get $H'$ leaves $\phi$ unaffected.

@@

In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
\multicolumn{3}{c|}{\multirow{2}{*}{Case}} & \multicolumn{1}{c|}{$x_{i}$} & \multicolumn{1}{c}{$L_{i}$} \\
    \multicolumn{3}{c|}{} & \multicolumn{1}{c|}{$x_{i} - x_{\lfloor n/2 \rfloor}$} & \multicolumn{1}{c}{$L_{i} - L_{\lfloor n/2 \rfloor}$} \\[0.5ex]\hline 
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
  \end{tabular}
  \caption{Lorenz curve elbow coordinates in the unital fragment.
  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
  Multiplication $2i$ is considered modulo $(n+1)$.
  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
  }
  \label{tab:lcsu_coord_elb_app}
\end{table}

@@

\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{i}$} & \multicolumn{1}{|c}{$L_{i}$} \\[0.5ex]\hline
   \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,p\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,1-p\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_-\left(2i;n,p\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,1-p\right)$ \\ \hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,1-p\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,p\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,1-p\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_+\left(2i;n,p\right)$ \\ \hline
  \end{tabular}
  \caption{Lorenz curve elbow coordinates in the unital fragment.
  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
  Multiplication $2i$ is considered modulo $(n+1)$.
  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
  }
  \label{tab:lcsu_coord_elb_app_alt}
\end{table}

@@

\subsection{Free energy dependent magic distillation bounds}\label{free-energy-bound-proof}
\label{app:main_proof}
Here we prove~\cref{thm:free-energy}, which bounds magic distillation rates in terms of free energies.

\begin{theorem}
	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$. We also allow pre/post-processing by local Clifford unitaries.

@@

Then the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
\begin{equation}\label{eq:rate_bounds_proof}
	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
\end{equation}
where $F$ is the free energy of $\tau$,  and 
\begin{equation}
	\phi = -\beta^{-1} \log \zeta
\end{equation}
with $\zeta$ given by the expressions
\begin{align}
	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
	\alpha_k &= \<E_k| A_{\x_\star} |E_k\>,
\end{align}
and $\x_\star = \arg\!\min W_\tau(\x)$. The primed variables are defined similarly for the output system.
\end{theorem}

>>>>

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{figs/test/R_vs_H.pdf}
    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = {\rm{diag}}(0,1,2)$ and $H' = (1-p-q){\rm{diag}}(0,1,2)+p{\rm{diag}}(1,2,0)+q{\rm{diag}}(2,0,1)$.
    }
    \label{fig:rvsh}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{figs/test/R_vs_A.pdf}
    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$.
    }
    \label{fig:rvsa}
\end{figure}

Performing the standard 3D-rotation matrix 
\begin{equation}
\begin{pmatrix}
\sin{\theta}\cos{\varphi} & \sin{\theta}\sin{\varphi} & \cos{\theta}\\
\cos{\theta}\cos{\varphi} & \cos{\theta}\sin{\varphi} & -\sin{\theta}\\
-\sin{\varphi} & \cos{\varphi} & 0
\end{pmatrix}
\end{equation}
on $H$ to get $H'$ leaves $\phi$ unaffected.
I didn't find any interesting case where $\phi \rightarrow \infty$, except of course when there is some $E_k \rightarrow \infty$. 
I looked through Hamiltonians which are convex combinations of phase-point operators and SHO (diagonal) Hamiltonians.

@@

In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
\multicolumn{3}{c|}{\multirow{2}{*}{Case}} & \multicolumn{1}{c|}{$x_{i}$} & \multicolumn{1}{c}{$L_{i}$} \\
    \multicolumn{3}{c|}{} & \multicolumn{1}{c|}{$x_{i} - x_{\lfloor n/2 \rfloor}$} & \multicolumn{1}{c}{$L_{i} - L_{\lfloor n/2 \rfloor}$} \\[0.5ex]\hline 
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
  \end{tabular}
  \caption{Lorenz curve elbow coordinates in the unital fragment.
  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
  Multiplication $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$.
  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
  }
  \label{tab:lcsu_coord_elb_app}
\end{table}

@@

\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{i}$} & \multicolumn{1}{|c}{$L_{i}$} \\[0.5ex]\hline
   \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,p\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,1-p\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_-\left(2i;n,p\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,1-p\right)$ \\ \hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,1-p\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,p\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,1-p\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_+\left(2i;n,p\right)$ \\ \hline
  \end{tabular}
  \caption{Lorenz curve elbow coordinates in the unital fragment.
  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
  Multiplication $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$.
  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
  }
  \label{tab:lcsu_coord_elb_app_alt}
\end{table}

@@

\subsection{Free energy dependent magic distillation bounds}\label{free-energy-bound-proof}
\label{app:main_proof}
Here we prove our main theorem, which bounds magic distillation rates in terms of free energies.

\begingroup
\def\thetheorem{\ref{thm:free-energy}}
\begin{theorem}
	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$. We also allow pre/post-processing by local Clifford unitaries.

@@

Then the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
\begin{equation}\label{eq:rate_bounds_proof}
	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
\end{equation}
where $F$ is the free energy of $\tau$,  and 
\begin{equation}
	\phi = -\beta^{-1} \log \zeta
\end{equation}
with $\zeta$ given by the expressions
\begin{align}
	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
	\alpha_k &= \<E_k| A_{\x_\star} |E_k\>,
\end{align}
and $\x_\star = \arg\!\min W_\tau(\x)$. The primed variables are defined similarly for the output system.
\end{theorem}
\addtocounter{theorem}{-1}
\endgroup
